\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}

\hypersetup{
colorlinks=true,
urlcolor=blue,
linkcolor=blue
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\begin{document}

%----------HEADING----------

\begin{center}
{\Huge \scshape Abhishek Kumar Singh} \ \vspace{2pt}

%----------HEADING----------

```
\small
+91 8542054587 $|$
\href{mailto:iitianabhisingh2244@gmail.com}{iitianabhisingh2244@gmail.com} $|$
\href{https://linkedin.com/in/abhisingh2244/}{linkedin.com/in/abhisingh2244} $|$
\href{https://github.com/abhisingh2244}{github.com/abhisingh2244} $|$
\href{https://leetcode.com/u/iitianabhisingh/}{leetcode.com/u/iitianabhisingh}
```

\end{center}


\end{center}

%-----------SUMMARY-----------

\section{Summary}

Senior Software Engineer with experience building performance-critical software using modern C++ on Linux and RTOS platforms. Strong background in systems programming, multithreading, concurrency, memory optimization, and real-time processing. Proven record of delivering reliable software in safety-critical environments and strong problem-solving ability demonstrated through global competitive programming achievements. Interested in low-latency systems, quantitative technology, and high-performance infrastructure engineering.

%-----------EDUCATION-----------

\section{Education}

\textbf{Kamla Nehru Institute of Technology} \hfill Jul 2019 -- May 2023

Bachelor of Technology, Computer Science and Engineering

CGPA: 8.2/10

%-----------EXPERIENCE-----------

\section{Experience}

\textbf{Senior Software Engineer} \hfill Sep 2023 -- Present

Boeing India, Bangalore

\begin{itemize}[leftmargin=*]
\item Developed latency-sensitive software components for Flight Deck Video Display systems using C++, Linux, RTOS and OpenGL.
\item Designed and optimized multithreaded processing pipelines for real-time video handling with end-to-end latency below 100 ms.
\item Reduced video freeze incidents by 90% through frame validation, memory management improvements and fault-tolerant processing logic.
\item Improved rendering throughput by 30% through cache-aware concurrency optimizations and efficient resource utilization.
\item Investigated and resolved complex production issues involving synchronization, memory usage and real-time scheduling.
\item Collaborated with global engineering teams and airline customers including Qatar Airways, Emirates, Singapore Airlines and Etihad.
\end{itemize}

\textbf{Quantitative Developer Intern} \hfill Sep 2022 -- Nov 2022

JP Morgan Chase & Co.

\begin{itemize}[leftmargin=*]
\item Worked with financial datasets and analytics workflows using Python and JavaScript.
\item Developed data visualization tooling and automated analysis pipelines.
\item Gained exposure to quantitative development concepts and financial technology systems.
\end{itemize}

\textbf{Cybersecurity Intern} \hfill May 2023 -- Jun 2023

Goldman Sachs

\begin{itemize}[leftmargin=*]
\item Evaluated enterprise security controls including firewalls, IDS/IPS systems and VPN infrastructure.
\item Performed security assessments of cryptographic workflows and network configurations.
\end{itemize}

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}

\textbf{Languages:}
C++, Python, JavaScript

\textbf{Systems:}
Linux, RTOS, Multithreading, Concurrency, Synchronization, Memory Management, IPC

\textbf{Programming Concepts:}
Data Structures, Algorithms, OOP, System Design, Performance Optimization

\textbf{Tools:}
Git, Docker, GDB, CMake, REST APIs

\textbf{Mathematics:}
Probability, Statistics, Linear Algebra

%-----------ACHIEVEMENTS-----------

\section{Achievements}

\begin{itemize}[leftmargin=*]
\item Top 0.5% globally in Google Code Jam.
\item Top 1% worldwide in Meta Hacker Cup.
\item Global Rank 2508 in Google Hash Code.
\item Top-5 Global Rank in CodeChef Starters and Lunchtime contests.
\item CodeChef 4-Star Programmer (Max Rating: 1908).
\end{itemize}

\end{document}
